Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-08 paper.tex

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here -mention hpc, data centre, cloud. 
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}

@@

\chapter{Other domains and general scientific worflow engines}
    \section{Taverna}
    Taverne is a scientific workflow engine designed to allow users to combine distributed web services, other service
    types (e.g. BioMart queries or R-scripts) and local scripts into complex analysis pipelines. The main goal of
    Taverna is to give a unified access to the plethora of services already existing on the web without requiring
    the user to download the services locally or to have knowledge on all of the platforms and programming languages
    the services are hosted under.

        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pegasus}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Geneflow}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Toil}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Thunder}

>>>>

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here -mention hpc, data centre, cloud. 
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item UK Biobank
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}

@@

\chapter{Other domains and general scientific worflow engines}
    \section{Taverna}
    Taverna is an open-source bioinformatics workflow engine, designed to allow users to combine distributed web services, other service
    types (e.g. BioMart queries or R-scripts) and local scripts into complex analysis pipelines. The main goal of
    Taverna is to give a unified access to the plethora of services already existing on the web without requiring
    the user to download the services locally or to have knowledge on all of the platforms and programming languages
    the services are hosted under.

        \subsection{Pipeline description}
        Workflows in Taverna are built by combining web services, local scripts and other services together. Web services compatible with
        Taverna must comply to the Web Service Description Language (WSDL) using the Simple Object Access Protocol (SOAP protocol). 
        These services can be added to the BioCatalogue or the Biodiveristy catalogue for sharing and reuse of the web services.

        Workflows can be built in the Taverna workbench. Taverna, through the help of the BioCatalogue and the Biodiversity Catalogue is
        able to provide the user with a variety of webservices to combine into workflows in a drag-and-drop fashion. Workflows may also be composed
        of sub-workflows. As service inputs and outputs may not match between services, shims are provided.
        Similarly to the services, the user-generated workflows can be uploaded the myExperiment repository to be shared with other user.

        \subsection{Pipeline execution}
        The workflows can be executed remotely utilizing the Taverna Server. The Taverna Server is a an application that provides the full library of possible workflows
        through webservices. It has an interface, known as the Taverna Player, that enables workflow execution to occur through a web-interface or through
        third-party clients. The Taverna Server, however, is limited in that it can only execute workflows available on the Server. Taverna Lite is an alternative to
        the Taverna Server which allows users to upload and execute workflows from myExperiment or elsewhere.

        \subsection{Debugging and provenance}
         Provenance capture is achieved through the Taverna Provenance Suite. Taverna does not capture provenance of the workflow definition, but generates a new
        UUID after each definition change. Workflow run provenance captures information on "individual processor iterations" and their respective inputs and outputs and
        stores this information in a database. The results can then be exported as a workflow trace or as a PROV-O RDF graph using the Taverna-PROV Plugin. The model format used
        for exported provenance uses both the W3C PROV model and Open Provenance Model format.

    \section{Pegasus}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Geneflow}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Toil}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Thunder}
